\documentclass{letter}[11pt]

\addtolength{\topmargin}{-1cm}
\addtolength{\textheight}{3cm}

\signature{Andrew Haven}
\address{Andrew Haven\\
drew.haven@stanford.edu\\
408-982-5425\\
}
\begin{document}

\begin{letter}{Akamai Technologies, Inc.\\
Cambridge, MA
}

\opening{To whom it may concern:}

I love to program.  It is where I am most comfortable and at home.  My work at Stanford has shown me that the future of computing will be distributed.  Networks of computers will be able to deliver orders of magnitude more power than any central mainframe.  Distributed computing has so many open questions and is under such active development that I expect it to be an exciting place to work over the next decade.

Distributed computing is an intriguing question because we know we have the resources available, but we need to be able to harness them such that they are flexible and scalable.  Answering these questions will open up more options in our computing, allowing applications to be distributed across continents and automatically scale to handle load, all while maintaining low latencies and security.  These are problems I want to help tackle.

My experience has taught me that creating extensible, maintainable systems is paramount for any large project.  The best way to tackle complexity is to reduce that complexity using powerful abstractions.  I pride myself on writing readable code and developing coherent APIs.  I am fluent with both object-oriented and functional programming.  I am seeking to work on even larger code bases so that I can see how my techniques scale, how they fail, and how others have overcome the obstacles before me.

My vocational background is largely in systems administration and web programming.  However,I have been programming since I was 10 and have never lost the love of burying myself in an afternoon of debugging and I yearn to have more code in my job.  In order to improve my programming I am currently working towards a Masters in CS at Stanford in my off hours.  Working while I study allows me to immediately and directly apply the things I learn, and gives me a context for everything I hear in the classroom.

I look forward to working with the original content distribution systems company and harnessing the power of highly distributed code.  I hope to hear from you soon as I am eager to start a new chapter in my career.

\closing{Sincerely,}
\end{letter}
\end{document}
