\documentclass{letter}[11pt]

\addtolength{\topmargin}{-1cm}
\addtolength{\textheight}{3cm}

\signature{Andrew Haven}
\address{Andrew Haven\\
drew.haven@stanford.edu\\
650.967.1827\\
}
\begin{document}

\begin{letter}{Advanced Micro Devices, Inc.\\
Palo Alto, CA
}

\opening{To whom it may concern:}

I love to program.  It is where I am most comfortable and at home.  Over the last four years of working and studying for a Masters in CS at Stanford, the most fun I have had programming was during the compilers course.  Compilers are one of the most complex and elegant pieces of software I've encountered.  The degree of complexity, abstractness, and correctness that are required is invigorating.  When I saw a posting for a compiler engineer dealing with OpenCL I had to apply, as another passion of mine is distributed, concurrent, and GPU computation.

I am passionate about programming, and to that end I am constantly seeking to improve at my craft and try new things.  I have dabbled in over a dozen languages over the years, and I frequently try new tools and techniques to improve my productivity.  My current job has me working largely alone.  I want to work with a team, integrating and collaborating with teammates to create larger and grander systems than I can achieve alone.

My vocational background is largely in systems administration and web programming, but that is only because it was the most active area of hiring when I entered the workforce with a degree in Physics, and at the time my focus was on network security.  I have been programming since I was 10 and have never lost the love of burying myself in an afternoon of debugging.  In order to improve my programming background I am currently working towards a Masters in CS at Stanford part-time through SCPD, and I intend to continue until I graduate.  Working while I study allows me to immediately and directly apply the things I learn, and gives me a context for everything I hear in the classroom.

I look forward to working with one of the major companies in the processor market, and to be on the forefront of technology tackling this new world of multi-core and multi-system computing.  I hope to hear from you soon as I am eager to start a chapter in my career.

\closing{Sincerely,}
\end{letter}
\end{document}
