\documentclass{letter}[11pt]

\addtolength{\topmargin}{-1cm}
\addtolength{\textheight}{3cm}

\signature{Andrew Haven}
\address{Andrew Haven\\
drew.haven@stanford.edu\\
408-982-5425\\
}
\begin{document}

\begin{letter}{23andMe, Inc.\\
Mountain View, CA
}

\opening{To whom it may concern:}

I love to program.  It is where I am most comfortable and at home.  I currently work for the Neurobiology department at Stanford as their IT and desktop support.  However, I constantly find myself finding excuses to write-up yet another web application or a quick tree-search if I can relate it any way to the work.  For example, I have written two different task tracking web applications to better keep track of my time.  In short, I want to spend more time with code, less time rebooting printers and configuring file servers.

23andMe is a company that is providing a very interesting service and growing.  I know you're going to need programming talent, you're going to need to be able to scale, and the nature of your data also means that you want to be secure.  I am actively interested and study both areas.  

My experience has taught me that creating extensible, maintainable systems is paramount for any large project.  The best way to tackle complexity is to reduce that complexity using powerful abstractions.  I pride myself on writing readable code and developing coherent APIs.  However, one thing I am missing is experience working on a team.  In most my projects so far I have had to work independently.  I am eager to work on a team, particularly to get feedback from the other team members.  The small teams I have heard about at 23andMe sound like a good mix of teamwork and independence.

You should know, I am currently working towards a Masters in CS at Stanford in my off hours.  Working while I study allows me to immediately and directly apply the things I learn, and gives me a context for everything I hear in the classroom.  I plan to continue my studies until completion, and I expect only a positive impact on my work

I look forward to working with a growing company with a primary web presence, particularly one that has ties to biology which is rare on the web.  I hope to hear from you soon as I am eager to start a new chapter in my career.

\closing{Sincerely,}
\end{letter}
\end{document}
