\documentclass{letter}[11pt]

\signature{Andrew Haven}
\address{Andrew Haven\\
drew.haven@stanford.edu\\
650.967.1827\\
}
\begin{document}

\begin{letter}{Facebook Inc.\\
Palo Alto, CA
}

\opening{To whom it may concern:}

I am currently "the IT guy" for the Neurobiology Department at Stanford
University, which means I do everything from programming data acquisition
software to systems administration to desktop support.  My time at Stanford has been great
for my personal development because it is so open to learning and I have
had nearly unlimited freedom to explore technologies.  This has helped me
narrow down the problem areas I want to work in. 

Now I want to be part of something bigger, a team managing millions of users
and petabytes of data.  I have learned that one of the biggest problems in computer science today
is parallelism and distributed computing.  I want to work in a place where
people have to deal with the issues of massive scaling every day.  I want
to make entire data centers of computers hum as they efficiently solve the
problems orders of magnitude larger than what we imagined ten years ago.

Facebook can provide all of this.  As one of the top ten visited sites on
the web, and growing, you must face these problems all the time.  You've
built up a world-class team to solve these problems and I want to be part
of that team.  You have a commitment to creating a great product using the
best tools.  All these things make Facebook an enticing place to work.

In three years I want to be able to look back and see how much I've
learned and how much I've accomplished since I started.  I think that can
happen at Facebook.

\closing{Sincerely,}
\end{letter}
\end{document}
