\documentclass{letter}[11pt]

\addtolength{\topmargin}{-1cm}
\addtolength{\textheight}{3cm}

\signature{Andrew Haven}
\address{Andrew Haven\\
drew.haven@stanford.edu\\
408-982-5425\\
}
\begin{document}

\begin{letter}{Google, Inc.\\
Mountain View, CA
}

\opening{To whom it may concern:}

I've spent the last five years working on the web and supporting people online.  Now I want to change pace and build the tools that make the web a better place to work and play.  I want to build things that have an impact on millions instead of hundreds.  I can think of no better place than Google.

My experience so far has been largely with system administration and web development, but I want to move to a fully development-focused career where I can spend more time buried in the code I love.  I've been spending the last five years learning different technologies--from C to Haskell and from ZFS to CouchDB--and am now half-way to an MS in computer science at Stanford.

I never want to stop learning, which is my primary motivation for a career change.  Google would be a perfect environment, as you foster creativity and critically examine every new technology.  I have always wanted to attend some of the excellent Google Tech Talks in person.

My strong learning drive, quick adaptation, and personal initiative would make me an great employee for Google.  I urge you to consider me for any openings in the engineering groups, particularly for web applications or infrastructure and engineering tools.  I look forward to working with the best and the brightest and I hope to hear from you soon.

\closing{Sincerely,}
\end{letter}
\end{document}
