\documentclass{letter}[11pt]

\addtolength{\topmargin}{-1cm}
\addtolength{\textheight}{3cm}

\signature{Andrew Haven}
\address{Andrew Haven\\
drew.haven@stanford.edu\\
408-982-5425\\
}
\begin{document}

\begin{letter}{Cryptic Studios\\
Los Gatos, CA
}

\opening{To whom it may concern:}

Programming is one of my two major hobbies.  I've spent the last five years working on the web, building sites and maintaining servers.  Now I want to change pace and begin building real server and client-side software.  I want to work on massively distributed software that will have an impact on millions instead of just hundreds.  As an MMO studio, Cryptic is a perfect place for me to reach that goal.

My experience so far has been largely with system administration and web development, but I want to move to a fully development-focused career where I can spend more time buried in the code I love.  I've been spending the last five years learning different technologies--from C to Haskell and from ZFS to CouchDB--and am now half-way to an MS in computer science at Stanford. My background is broad, and I learn quickly.

My second major hobby is gaming.  I am an avid fan of RPGs; both the single and multi-player variants.  With Cryptic being one of the few studios with repeated MMO success, it would be a dream to be able to work on the software I enjoy.  I would be able to unite my passion for gaming and programming.

My strong learning drive, quick adaptation, and personal initiative would make me an great employee for Cryptic.  I urge you to consider me for the currently open software engineering positions.  I look forward to working with the best and the brightest and I hope to hear from you soon.

\closing{Sincerely,}
\end{letter}
\end{document}
